Pan-cancer analysis

### 2021-03-10 src/manuscript_figures.Rmd
drop analyses that are not part of the manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source('/data/local/buyar/arcas/subtyping_paper/src/common_functions.R')
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
theme_set(ggpubr::theme_pubclean())

inputDir <- '/data/local/buyar/arcas/subtyping_paper/pancancer/output/'
assay_dir <- '/data/local/buyar/arcas/subtyping_paper/pancancer/assays/'
surv <- do.call(rbind, readRDS('/data/local/buyar/pancancer_diagnostics/data/GDCdata_processed2/TCGA.surv.RDS'))
projectDict <- sapply(yaml::read_yaml('/data/local/buyar/arcas/subtyping_paper/data/projects.dict.yaml'), 
                      function(x) gsub(' ', '', unlist(strsplit(x, ','))))
tcga_subtypes <- process_tcga_subtypes()
```

@@

# Classify metastatic samples

Use TCGA-SKCM as case study to see if we can predict which samples are metastatic and which ones are primary
We have multi-omics data from 360 metastatic tumors and 100 primary tumors (distinct group of patients)
```{r, eval = FALSE}
# read batch info to see which patient samples are metastatic
batches <- do.call(rbind, lapply(dir(assay_dir, "TCGA-SKCM.*info.tsv", full.names = T),
                  data.table::fread))
# get sample types from sample barcodes
st <- get_tcga_sample_types(batches$V1)
st$bcr_patient_barcode <- sub("^(.{12}).+$", "\\1", st$barcode)
# primary tumors: TP, metastatic tumors: TM
st <- unique(st[sampletype %in% c('TP', 'TM')][,2:3])

skcm_stats <- do.call(rbind, lapply(names(LFs), function(tool) {
  message(tool)
  M <- LFs[[tool]][['TCGA-SKCM.cnv_gex_meth_mut']]
  y <- st[match(rownames(M), bcr_patient_barcode)]$sampletype
  M <- M[!is.na(y),]
  y <- y[!is.na(y)]
  #res <- predict_cluster_labels(M, y, num.trees = 2000)
  res <- predict_cluster_labels_glmnet(M, y)
  # plot_tsne(M, y)
  res$method <- tool
  return(res)
}))

# with glmnet 
ggplot(skcm_stats[label == 'TM'], aes(x = method, y = auc)) + 
  geom_bar(aes(fill = method), stat = 'identity') + 
  geom_errorbar(aes(ymin = auc.lower, ymax = auc.upper), width = 0.2) + 
  labs(y = 'AUC',x = '') + theme(legend.title = element_blank())

# plot maui LFs predictive of metastatic/primary tumor
M <- LFs$maui_factors[['TCGA-SKCM.cnv_gex_meth_mut']]
y <- st[match(rownames(M), bcr_patient_barcode)]$sampletype
M <- M[!is.na(y),]
y <- y[!is.na(y)]
dt <- get_factor_specific_variables(M, y)
top_vars <- get_top_by_label(dt[padj < 0.05][order(padj)], 'ref_cl', topN = 5)[['variable']]

plot_tsne(M[,top_vars], y)

df <- data.frame(M[,top_vars])
df$y <- as.factor(y)
fit <- ranger::ranger(seed = 42, formula = y ~ ., data = df, probability = T, num.trees = 1000)

cp <- data.frame(fit$predictions)
rownames(cp) <- rownames(df)
cp$type <- st[match(rownames(cp), bcr_patient_barcode)]$sampletype

# find metastatic samples that look like primary tumor samples
d1 <- cp[cp$type == 'TM' & cp$TM > 0.7,]
d1$confident <- 'confident_metastatic'
d2 <- cp[cp$type == 'TM' & cp$TM < 0.7,]
d2$confident <- 'not_confident_metastatic'
plot_survival(surv, rbind(d1, d2)[,'confident',drop = F], duration_col = 'OS.time',
              event_col = 'OS')

# check cancer state scores to see if unconfident metastatic samples have similar scores as primary ones
dataDir <- '/data/local/buyar/arcas/subtyping_paper/data/geneset_scores/singscore/msigdb_canonical_pathways/'
files <- dir(dataDir, '.scores.csv', full.names = T)
scores <- do.call(rbind, sapply(simplify = F, files, function(x) {
 data.table::fread(x)
}))
colnames(scores)[1] <- 'bcr_patient_barcode'

cp$group <- 'primary'
cp[cp$type == 'TM' & cp$TM >= 0.7,]$group <- 'confident_metastatic'
cp[cp$type == 'TM' & cp$TM < 0.7,]$group <- 'not_confident_metastatic'

# get cancer state scores
dt <- scores[match(rownames(cp), bcr_patient_barcode),]
M <- as.matrix(dt[,-1])
rownames(M) <- dt$bcr_patient_barcode

dt <- get_factor_specific_variables(M, as.factor(cp$group))

B <- get_basis_matrix(M, cp$group)
#B2 <- apply(B, 2, function(x) x/max(x)+max(x)/4)
#pheatmap(B2)
pheatmap(B[,unique(dt[padj < 0.05]$variable)])

# what are the genes that distinguish confident metastatic from 
M <- LFs$maui_factors$`TCGA-SKCM.cnv_gex_meth_mut`
plot_label_specific_vars(M, cp$group, top_vars_per_label = 5)
dt <- get_factor_specific_variables(M, cp$group)
top <- get_top_by_label(dt[padj < 0.05][order(padj)], 'ref_cl', 5)

# Show subtypes depend on the objective

Patients clustering depend on the objective of stratification

```{r}
clin_factors <- c('age_at_initial_pathologic_diagnosis', 'gender', 'ajcc_pathologic_tumor_stage')

project <- 'pan-gastrointestinal'
datatype <- 'cnv_gex_meth_mut'
experiment <- paste0(project, '.', datatype)

M <- LFs$maui_factors[[experiment]]
M <- t(subset_features_by_variance(t(remove_redundant_variables(M)), topN = 20))

clin <- process_clinical_covariates(rownames(M))
clin <- subset(clin, select = intersect(colnames(clin), clin_factors))

pfi_vars <- get_prognostic_covariates(surv, clin, M, event_col = 'PFI', duration_col = 'PFI.time')
pfi_clust <- get_kmeans_subtypes(M[,unique(pfi_vars$variable)], k_vals = 3:8, min_cluster_size = 0)
pfi_k <- names(which.min(sapply(colnames(pfi_clust), function(x) plot_survival(surv, pfi_clust[,x,drop = F], 'PFI.time', 'PFI', T))))

os_vars <- get_prognostic_covariates(surv, clin, M, event_col = 'OS', duration_col = 'OS.time')
os_clust <- get_kmeans_subtypes(M[,unique(os_vars$variable)], k_vals = 3:8, min_cluster_size = 0)
os_k <- names(which.min(sapply(colnames(os_clust), function(x) plot_survival(surv, os_clust[,x,drop = F], 
                                                                             'OS.time', 'OS', T))))

# combine with known pan-gi subtype annotation

df <- merge(pfi_clust[,pfi_k,drop = F], os_clust[,os_k,drop = F], by = 'row.names')
df$subtype <- tcga_subtypes[match(df$Row.names, bcr_patient_barcode)]$Subtype_Selected

tsne <- plot_tsne(remove_redundant_variables(M), returnData = T)

df$tSNE1 <- tsne[df$Row.names,]$tSNE1
df$tSNE2 <- tsne[df$Row.names,]$tSNE2

mdf <- melt(df, id.vars = c('Row.names', 'tSNE1', 'tSNE2'))

ggplot(mdf, aes(x = tSNE1, y = tSNE2)) + 
  geom_point(aes(color = as.factor(value))) + 
  facet_wrap(~ variable, nrow = 1)
```

# predict mutational signatures
```{r}
# import mutational signature data
mutsig <- data.table::fread('/data/local/buyar/pancancer_diagnostics/data/mutational_signatures/signature_profile_sample.txt')
mutsig$Tumor_Sample_Barcode <- gsub("\\.", "-", mutsig$Tumor_Sample_Barcode)
# only keep TCGA samples
mutsig <- mutsig[grep('TCGA', Tumor_Sample_Barcode)]
dt <- data.table::dcast(mutsig, Tumor_Sample_Barcode ~ Signature, value.var = 'Contribution')

cl <- parallel::makeCluster(30) 
parallel::clusterExport(cl, varlist = c('dt', 'LFs'))
res <- do.call(rbind, pbapply::pbsapply(simplify = F, cl = cl, unique(mutsig$Signature), function(x) {
  require(data.table)
  source('/data/local/buyar/arcas/subtyping_paper/src/common_functions.R')
  r <- do.call(rbind, lapply(names(LFs), function(m) {
    message(m)
    M <- LFs[[m]]$pancancer.cnv_gex_meth_mut
    s <- predict_numerical_glmnet(M, dt[match(rownames(M), Tumor_Sample_Barcode)][[x]])
    s$tool <- m
    return(s)
  }))
  r$sig <- x
  return(r)
}))
parallel::stopCluster(cl)

ggplot(res, aes(x = reorder(sig, Rsquare), y = Rsquare)) + 
  geom_bar(stat = 'identity', aes(fill = tool), position = 'dodge') + 
  coord_flip() + labs(x = '')

df <- melt(dcast(res, sig ~ tool, value.var = 'Rsquare'), 
                id.vars = c('sig', 'maui_factors'))

ggplot(df, aes(x = maui_factors, y = value)) + geom_point() + 
  facet_wrap(~ variable, nrow = 1) + 
  geom_abline(slope = 1)
```

# predictability of clinical factors

```{r, eval = FALSE}
# predict tumor purity using latent factors 
res <- do.call(rbind, lapply(names(LFs), function(tool) {
  message(tool)
  M <- LFs[[tool]][['pancancer.cnv_gex_meth_mut']]
  y <- process_clinical_covariates(rownames(M))[,'tumor_purity_IHC']
  res <- predict_numerical_glmnet(M, y)
  res$method <- tool
  return(res)
}))

# predict tumor stage for pan-gi 
pangi_stats <- predict_labels(LFs, surv, tcga_subtypes, 
                              'pan-gastrointestinal', 'cnv_gex_meth_mut', label.type = 'clinical')
ggplot(pangi_stats[label.type == 'ajcc_pathologic_tumor_stage'][label != 'Undefined'], aes(x = label, y = test_auc)) + 
  geom_bar(aes(fill = method), stat = 'identity', position = 'dodge') +
  coord_flip()

# tumor stage 
label <- 'age_at_initial_pathologic_diagnosis'
experiment <- 'TCGA-BRCA.cnv_gex_meth_mut'
stats <- do.call(rbind, lapply(names(LFs), function(tool) {
  message(tool)
  M <- LFs[[tool]][[experiment]]
  y <- process_clinical_covariates(rownames(M))[[label]]
  M <- M[!is.na(y),]
  y <- y[!is.na(y)]
  #res <- predict_cluster_labels(M, y)
  res <- predict_numerical_glmnet(M, y)
  res$method <- tool
  return(res)
}))
# with glmnet multi-label pred
ggplot(stats, aes(x = method, y = Accuracy)) + 
  geom_bar(stat = 'identity', aes(fill = method)) + 
  geom_errorbar(aes(ymin = AccuracyLower, ymax = AccuracyUpper), width = 0.2)

# predictability of cancer states

```{r, eval = F}
# read cancer sea gene set scores
#dataDir <- '/data/local/buyar/pancancer_diagnostics/data/geneset_scores/cancersea'
#files <- dir(dataDir, '.scores.csv', full.names = T)
#scores <- do.call(rbind, sapply(simplify = F, files[1:3], function(x) {
#  data.table::fread(x)
#}))
#colnames(scores)[1] <- 'bcr_patient_barcode'

scores <- readRDS('/data/local/buyar/arcas/subtyping_paper/data/mogsa_scores/MOGSA_scores.RDS')
scores <- do.call(rbind, lapply(scores$cnv_gex_meth_mut, function(x) data.table(x, keep.rownames = T)))
colnames(scores)[1] <- 'bcr_patient_barcode'

# elastic net regression on pathway scores usign LFs as input
predict_scores <- function(scores, LFs, label, experiment)
  do.call(rbind, lapply(names(LFs), function(tool) {
    message(tool)
    M <- LFs[[tool]][[experiment]]
    y <- scores[match(rownames(M), bcr_patient_barcode)][[label]]
    M <- M[!is.na(y),]
    y <- y[!is.na(y)]
    res <- predict_numerical_glmnet(M, y)
    res$method <- tool
  return(res)
}))

labels <- c('ANGIOGENESIS', 'GLYCOLYSIS', 'COAGULATION', 'DNA_REPAIR', 
            'HYPOXIA', 'ESTROGEN_RESPONSE_EARLY', 'ESTROGEN_RESPONSE_LATE' ,
            'EPITHELIAL_MESENCHYMAL_TRANSITION')
brca_scores <- do.call(rbind, lapply(labels, function(l) {
  message(l)
  df <- predict_scores(scores, LFs, l, 'TCGA-BRCA.cnv_gex_meth_mut')
  df$label <- l
  return(df)
}))

ggplot(brca_scores, aes(x = label, y = Rsquare)) + 
  geom_bar(stat = 'identity', aes(fill = method), position = 'dodge') + 
  coord_flip()
```

# pan-cancer survival factors 
```{r, eval = FALSE}
# factors to use in the model
clin_factors <- c('age_at_initial_pathologic_diagnosis', 'gender', 'ajcc_pathologic_tumor_stage', 
                  'PFI', 'PFI.time')
experiment <- 'pancancer.cnv_gex_meth_mut'
res <- do.call(rbind, lapply(names(LFs), function(tool) {
  message(tool)
  M <- LFs[[tool]][[experiment]]
  clin <- process_clinical_covariates(rownames(M))
  clin <- get_surv_df(surv, clin[,intersect(colnames(clin), clin_factors),drop = F])
  cl <- parallel::makeCluster(50)
  parallel::clusterExport(cl, varlist = c('clin', 'M'))
  res <- do.call(rbind, pbapply::pblapply(cl = cl, 1:100, function(i) {
    source('/data/local/buyar/arcas/subtyping_paper/src/common_functions.R')
    require(data.table)
    s <- sample(rownames(M), 0.5 * nrow(M))
    dt <- get_prognostic_covariates(clin[s,], M[s,])
    dt$i <- i
    return(dt)
  }))
  parallel::stopCluster(cl)
  res$method <- tool
  return(res)
}))

# get top factor per method
plots <- sapply(simplify = F, names(LFs), function(tool) {
  M <- LFs[[tool]][[experiment]]
  top_fac <- res[method == tool][,length(unique(i)),by = 'variable'][order(V1, decreasing = T)]$variable[1:3]
  cowplot::plot_grid(plotlist = lapply(top_fac, function(x) {
     p <- plot_survival(surv, data.frame('cl' = ifelse(M[,x] > median(M[,x]), 
                                             'high', 'low')))
     p$plot
  }), nrow = 1)
})
dev.off()
cowplot::plot_grid(plotlist = plots, nrow = 3, labels = names(plots))

M <- LFs[[tool]][[experiment]]
plot_tsne(M, M[,'LF32'])
```

<!-- Cluster samples into k = number of cancer types in the project -->

<!-- ```{r} -->
<!-- cl <- parallel::makeCluster(20) -->
<!-- parallel::clusterExport(cl, varlist = c('LFs', 'projectDict')) -->
<!-- clusters <- sapply(simplify = F, names(LFs), function(tool) { -->
<!--   message("Clustering top ",tool) -->
<!--   pbapply::pbsapply(cl = cl, simplify = F, names(LFs[[tool]]), function(experiment) { -->
<!--     message(experiment) -->
<!--     project <- strsplit(experiment, '\\.')[[1]][1] -->
<!--     datatype <- strsplit(experiment, '\\.')[[1]][2] -->
<!--     source('/data/local/buyar/arcas/subtyping_paper/src/common_functions.R') -->
<!--     require(data.table) -->
<!--     M <- LFs[[tool]][[experiment]] -->
<!--     if(tool == 'maui_factors') { -->
<!--       M <- t(subset_features_by_variance(t(M), topN = 10)) -->
<!--     } else { -->
<!--       M <- M[,head(colnames(M), 10),drop = F] -->
<!--     } -->
<!--     val <- c('internal')  -->
<!--     #if(ncol(M) > 2) {val <- c('internal', 'stability')} -->
<!--     #k <- length(projectDict[[project]]) -->
<!--     res <- clValid::clValid(obj = M, -->
<!--                           nClust = 3:10, -->
<!--                           clMethods = 'kmeans', -->
<!--                           validation = val, -->
<!--                           maxitems = 10000, -->
<!--                           nstart = 1000) -->
<!--     memberships <- as.data.frame(do.call(cbind, lapply(res@clusterObjs[['kmeans']], function(x) x[['cluster']]))) -->
<!--     colnames(memberships) <- paste0('k', colnames(memberships)) -->
<!--     stats <- as.data.table(res@measures)[V1 %in% c('Silhouette', 'APN')] -->
<!--     colnames(stats) <- c('metric', 'k', 'clustering_method', 'score') -->
<!--     return(list('clustering_stats' = stats, 'cluster_memberships' = memberships)) -->
<!--   }) -->
<!-- }) -->
<!-- parallel::stopCluster(cl) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- stats <- do.call(rbind, lapply(names(clusters), function(tool) { -->
<!--   do.call(rbind, lapply(names(clusters[[tool]]), function(experiment) { -->
<!--       cancer_type <- strsplit(experiment, "\\.")[[1]][1] -->
<!--       datatypes <- strsplit(experiment, "\\.")[[1]][2] -->
<!--       stats <- clusters[[tool]][[experiment]][['clustering_stats']] -->
<!--       stats$cancer_type <- cancer_type -->
<!--       stats$datatypes <- datatypes -->
<!--       stats$method <- tool -->
<!--       return(stats) -->
<!--   })) -->
<!-- })) -->
<!-- ``` -->

<!-- clustering metrics -->
<!-- ```{r} -->
<!-- ggboxplot(stats[datatypes == 'cnv_gex_mut'], x = 'method', y = 'score',  -->
<!--           add = 'jitter', facet.by = 'metric', color = 'method') -->
<!-- ``` -->

<!-- Find out how much the cluster labels correspond to cancer types  -->
<!-- ```{r} -->
<!-- cl <- parallel::makeCluster(20) -->
<!-- parallel::clusterExport(cl, varlist = c('clusters', 'projectDict', 'surv', )) -->
<!-- # compute mutual information stats (between cluster labels and cancer types) -->
<!-- MI_stats <- do.call(rbind, sapply(simplify = F, names(clusters), function(tool) { -->
<!--   message("computing MI for ",tool) -->
<!--   do.call(rbind, pbapply::pbsapply(cl = cl, simplify = F, names(clusters[[tool]]), -->
<!--                                    function(experiment) { -->
<!--     message(experiment) -->
<!--     project <- strsplit(experiment, '\\.')[[1]][1] -->
<!--     datatype <- strsplit(experiment, '\\.')[[1]][2] -->
<!--     source('/data/local/buyar/arcas/subtyping_paper/src/common_functions.R') -->
<!--     require(data.table) -->
<!--     k <- stats[method == tool][cancer_type == project][datatypes == datatype][,.SD[which.max(score)]]$k -->
<!--     clust <- clusters[[tool]][[experiment]][['cluster_memberships']][,paste0('k',k),drop=F] -->
<!--     labels <- surv[match(rownames(clust), bcr_patient_barcode)]$project -->

<!--     data.table('method' = tool, 'project' = project, 'datatypes' = datatype,  -->
<!--                'cramersV' = compute_cramers_V(cbind(clust, labels))[['cramersV']],  -->
<!--                'ARI' = aricode::ARI(clust[,1], labels),  -->
<!--                'AMI' = aricode::AMI(clust[,1], labels)) -->
<!--                                    })) -->
<!--   })) -->
<!-- parallel::stopCluster(cl) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ggboxplot(MI_stats[datatypes == 'cnv_gex_mut'],  -->
<!--           x = 'method', y = 'AMI',  -->
<!--           add = 'jitter') +  -->
<!--     stat_compare_means(method = 'wilcox.test', paired = T, method.args = list('alternative' = 'greater'),  -->
<!--                      comparisons = list(c('maui_factors', 'mofa_factors'),  -->
<!--                                         c('maui_factors', 'pca_factors'))) + -->
<!--   labs(title = 'One-vs-all test-AUC by cancer type') -->

<!-- ``` -->

<!-- Unsupervised clustering experiment -->
<!-- ```{r} -->
<!-- get_plot <- function(M, plot.type = 'cancertype') { -->

<!--   df <- plot_tsne(M) -->
<!--   if(plot.type == 'cancertype') { -->
<!--     df$tcga <- surv[match(rownames(df), bcr_patient_barcode)]$project -->
<!--   } else if (plot.type == 'subtype') { -->
<!--     df$tcga <- tcga_subtypes[match(rownames(df), bcr_patient_barcode)]$Subtype_Selected -->
<!--   } -->
<!--   clust <- get_kmeans_subtypes(M[rownames(df),], k_vals = length(unique(df$tcga)), 0) -->
<!--   df$maui <- as.factor(clust[rownames(df),]) -->

<!--   p <- ggplot(df, aes(x = tSNE1, y = tSNE2))   -->
<!--   p1 <- p + geom_point(aes(color = maui)) + -->
<!--     geom_text_repel(data = get_centroid(df[,1:2], df$maui),  -->
<!--               aes(x,y,label = text.label), size = 6) -->
<!--   p2 <- p + geom_point(aes(color = tcga)) +  -->
<!--           geom_text_repel(data = get_centroid(df[,1:2], df$tcga),  -->
<!--               aes(x,y,label = text.label), size = 5) -->

<!--   p <- cowplot::plot_grid(p1, p2) -->
<!--   # also compute mutual information -->
<!--   ami <- aricode::AMI(df$tcga, df$maui) -->
<!--   return(list('p' = p, 'ami' = ami)) -->
<!-- } -->

<!-- pr <- 'pancancer' #'pancancer' # 'pan-gastrointestinal' -->
<!-- e <- paste0(pr, '.cnv_gex_meth_mut') -->
<!-- M <- LFs$maui_factors[[e]] -->
<!-- ct <- surv[match(rownames(M), bcr_patient_barcode)]$project -->
<!-- st <-  tcga_subtypes[match(rownames(M), bcr_patient_barcode)]$Subtype_Selected -->

<!-- dt.ct <- get_factor_specific_variables(M, ct) -->
<!-- ct_vars <- unique(get_top_by_label(dt.ct[padj < 0.05][order(padj)], label.type = 'ref_cl', 2)[['variable']]) -->
<!-- dt.st <- get_factor_specific_variables(M, st) -->
<!-- st_vars <- unique(get_top_by_label(dt.st[padj < 0.05][order(padj)], 'ref_cl', 2)[['variable']]) -->

<!-- # LFs with most variance -->
<!-- top_vars <- rownames(subset_features_by_variance(t(M), topN = 42)) -->
<!-- # using top vars will cause the clusters dominated by the major component to dominate -->

<!-- p1 <- get_plot(M, 'cancertype') # use all factors  (unsupervised) -->
<!-- p2 <- get_plot(M[,top_vars], 'cancertype') # use top most variable factors (unsupervised) -->
<!-- p3 <- get_plot(M[,ct_vars], 'cancertype') # use cancer type specific factor (supervised ) -->
<!-- p4 <- get_plot(remove_redundant_variables(M, cutoff = 0.6), 'cancertype') # (unsupervised) -->
<!-- p5 <- get_plot(LFs$pca_factors[[e]]) # pca -->
<!-- p5.1 <- get_plot(LFs$pca_factors[[e]][,1:10]) # pca -->
<!-- p5.2 <- get_plot(LFs$pca_factors[[e]][,1:20]) # pca -->
<!-- p5.4 <- get_plot(LFs$pca_factors[[e]][,1:40]) -->

<!-- p6 <- get_plot(LFs$mofa_factors[[e]]) # mofa -->

<!-- ps <- lapply(c(5:8/10), function(r) { -->
<!--   get_plot(remove_redundant_variables(M, cutoff = r), 'cancertype') -->
<!-- }) -->

<!-- dt <- do.call(rbind, lapply(experiments, function(e) { -->
<!--   x <- LFs$maui_factors[[e]] -->
<!--   y <- remove_redundant_variables(x, cutoff = 0.6) -->
<!--   data.table('before' = ncol(x), 'after' = ncol(y), 'n' = nrow(x), 'exp' = e,  -->
<!--              'redundant' = ncol(x) - ncol(y)) -->
<!-- })) -->

<!-- p5 <- ggscatter(dt, x = 'n', y = 'redundant', add = 'reg.line') + -->
<!--    stat_cor(label.x = 400, label.y = 80, size = 6) + -->
<!--   labs(x = 'Number of samples', y = 'Percentage of redundant LFs') + -->
<!--   stat_regline_equation(label.x = 400, label.y = 75, size = 6) +  -->
<!--   geom_text_repel(aes(label = gsub('.cnv_gex_meth_mut', '', exp))) -->

<!-- ``` -->

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
settings <- yaml::read_yaml('/data/local/buyar/arcas/pancancer_multiomics_manuscript/settings.yaml')
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
theme_set(ggpubr::theme_pubclean())

inputDir <- '/data/local/buyar/arcas/pancancer_multiomics_manuscript/output'
assay_dir <- settings$assay_output$folder
surv <- do.call(rbind, readRDS(settings$surv))
projectDict <- sapply(yaml::read_yaml(settings$projectDict), 
                      function(x) gsub(' ', '', unlist(strsplit(x, ','))))
tcga_subtypes <- process_tcga_subtypes()
```

@@
